Creating the ``r params$package_name`` R package

### 2025-07-23 create-FSHybridPLS.Rmd
compute_gram_matrix_deriv2

We check the following cases:

| Case | Test                 | Expectation                             |
|------|----------------------|------------------------------------------|
| 1    | Orthogonal (Fourier) | Gram matrix ≈ diagonal                  |
| 2    | Constant             | Single value equals interval length (1) |
| 3    | Invalid              | Raises informative error                |
| 4    | Narrow support       | Mostly low off-diagonal entries         |

>>>>

### compute_gram_matrix_deriv2
```{r}
# Helper function to compute the Gram matrix of the second derivatives of basis functions
# This function assumes 'basisobj' is an 'fda' package basis object.
compute_gram_matrix_deriv2 <- function(basisobj) {
  # Get the range of the basis
  basis_range <- basisobj$rangeval

  # Create a function to evaluate the second derivative of a basis function
  # This uses the 'eval.basis' function with 'Lfdobj = 2' for second derivative.
  deriv2_basis_eval_fun <- function(t_vec) {
    eval.basis(t_vec, basisobj, Lfdobj = 2)
  }

  # Numerically integrate the product of second derivatives of basis functions
  # This is a general approach for computing inner products.
  # For specific basis types (e.g., B-splines), there might be more efficient
  # analytical solutions, but this approach is robust.
  nbasis <- basisobj$nbasis
  gram_matrix_deriv2 <- matrix(0, nbasis, nbasis)

  for (j in 1:nbasis) {
    for (k in 1:nbasis) {
      # Define the integrand: product of the j-th and k-th second derivatives
      integrand <- function(t) {
        deriv2_basis_eval_fun(t)[, j] * deriv2_basis_eval_fun(t)[, k]
      }
      # Integrate over the basis range
      gram_matrix_deriv2[j, k] <- integrate(integrand, lower = basis_range[1], upper = basis_range[2])$value
    }
  }
  return(gram_matrix_deriv2)
}
```
